Clumpiness and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy

### 2017-02-23 paper/letter.tex
subsections

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
Ouflows and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Mar\'ia Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a a
flux integral of one.
We then build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models, and then select for further analysis the best
$1\%$ models according to the lowest $\chi^2$ values.
These best $50$ models have a large span in $\chi^2$ going from values
of $1000$ to $3000$.

@@

Figure 1. summarizes our findings.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for a
rotating homogeneous gas sphere (thin line) and the multiphase
model (thick line). 
This is the first time that these models have been introduced with
success to explain an observed \lya\ profile.

@@

 For the current work, we computed the $\chi^2$ for each of the $2500$
models. We selected the best $50$ models with the lowest $\chi^2$. The
$\chi^2$ gap in those $50$ models is close to $3000$, the lowest
$\chi^2$ is close to $1200$. The total number of degrees of freedom is
$104$.

Then we performed a Kolmogorov-Smirnov test to compare each parameter
distribution in the best $50$ models against the parent distribution
of $2500$ models. 
If we obtain a p-value $<0.05$ for a given parameter, we conclude that
this parameter does influence the $\chi^2$ fit, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.

The best values for those parameters that we report here correspond to
the values that produce the minimum
$\chi^2$. The 1-$\sigma$ uncertainty comes from a parabolic fit to the
$\chi^2$ as a function of $v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
$P_{\rm cl}$ around its corresponding minimum.
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
Clumpiness and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Mar\'ia Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a a
flux integral of one.
We then build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models, and then select for further analysis the best
$1\%$ models according to the lowest $\chi^2$ values.
The
$\chi^2$ gap in those $25$ models is close to $3000$, the lowest
$\chi^2$ being close to $1200$.
The total number of degrees of freedom is
$104$.

Then we performed a Kolmogorov-Smirnov test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
this parameter does influence the $\chi^2$ fit, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.

The best values for the influential parameters correspond to
the values that produce the minimum
$\chi^2$.
The 1-$\sigma$ uncertainty comes from a parabolic fit to the
$\chi^2$ as a function of $v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
$P_{\rm cl}$ around its corresponding minimum.

@@

Figure 1. summarizes our findings.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for a
urotating homogeneous gas sphere (thin line) and the multiphase
model (thick line).

In spite of the simplicity of our models, this is the first time that
the main \tol\ features can be reproduced: a wide, centered,
single-peaked \lya\ line.
This result does not demonstrate that our models are unique to
reproduce \tol's features, but is a significant step forward to
understand why this source is atypical.

\subsection{Multiphase ISM}
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

@@
